Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
diction. dashes.

The Scantegrity system \cite{scantegrity_ii} (technically, we consider an updated version known as
Scantegrity II) is designed to provide verifiability atop existing in-person voting systems that
rely on fill-in ballots that are processed via optical scan.

@@

Some selection of persons associated with the electing body use a secret-sharing scheme to protect a
secret pseudorandom number generator key. Table P lists every ballot that will be produced for the
election and specifies exactly what code is used for each candidate per ballot. These codes are
generated using the pseudorandom generator and \emph{must} be kept secret.

@@

Table R is the ``heart'' of the Scantegrity Tables: it maps cast ballots in Table Q to tally marks
in Table S. Each row in Table R maps a single cell in Q to a single cell in S, and the order of
these mappings is pseudorandom (though the mappings must obey the data specified in Table P for vote
correctness).

>>>>

The Scantegrity system \cite{scantegrity_ii} -- we consider an updated version technically known as
Scantegrity II -- is designed to provide verifiability atop existing in-person voting systems that
rely on fill-in ballots processed via optical scan.

@@

Some selection of officials conducting the election use a secret-sharing scheme to protect a
secret pseudorandom number generator key. Table P lists every ballot that will be produced for the
election and specifies exactly what code is used for each candidate per ballot. These codes are
generated using the pseudorandom generator and \emph{must} be kept secret.

@@

Table R comprises the heart of the Scantegrity Tables: it maps cast ballots in Table Q to tally marks
in Table S. Each row in Table R maps a single cell in Q to a single cell in S, and the order of
these mappings is pseudorandom (though the mappings must obey the data specified in Table P for vote
correctness).
